New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/weakschur.tex
Modifs
Phrase intro Subsection 3.3

\begin{proof}[\textsc{Proof.}]
By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
The result is then obtained by simplying the equality. \\
\end{proof}

@@

We now proceed to state and prove the main result of this article.

@@

\begin{align}
	WS(n + 1) &\geqslant  4\,S(n)  +  2 \label{WS(n+1)} \\
	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} \\
	WS(n + 3) &\geqslant  42\,S(n)  +  24 \label{WS(n+3)} \\
	WS(n + 4) &\geqslant  132\,S(n)  +  26 \label{WS(n+4)}
\end{align}

Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}. 
Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
sophistication explained in Subsection \ref{ConstructionWS} in order to add
the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 
inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.

>>>>

\begin{proof}[\textsc{Proof.}]
By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
The result is then obtained by simplifying the equality. \\
\end{proof}

@@

Having established these properties, we now have everything we need to state and prove our main result. We proceed to do so
in the next subsection.

@@

\begin{align}
	WS(n + 1) &\geqslant  4\,S(n)  +  2 \label{WS(n+1)} \\
	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} 
\end{align}

Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}.

\begin{align}
	WS(n + 3) &\geqslant  42\,S(n)  +  24 \label{WS(n+3)} \\
	WS(n + 4) &\geqslant  132\,S(n)  +  26 \label{WS(n+4)}
\end{align}

Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
sophistication explained in Subsection \ref{ConstructionWS} in order to add
the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 
inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
